Preliminary Survey on Statistics and Software

### 2019-08-27 static/homeworks/00-preliminary-survey.Rmd
Fix github link for updates, assignments shortcode to remove due dates; add preliminary survey PDF

---
title: "Preliminary Survey on Statistics and Software"
editor_options: 
  chunk_output_type: console
---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(pander)
source(file.path(here::here(), "lib", "graphics.R"))
```

@@

- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/homeworks/00-preliminary-survey.pdf)

@@

# 1

Using the following sample data:

@@

a. Find the median. 
b. Calculate the sample mean, $\bar{x}$
c. Calculate the sample standard deviation, $s$

# 2

For a fair, six-sided die:

a. What is the probability of rolling a 5?
b. What is the probability of rolling an even number?
c. What is the probability of rolling an even number or a 3?
d. If you have two fair dice, what is the probability of rolling a 6 on both dice?

# 3

Hedge fund A earns an average rate of return of 2.5% per year with a standard deviation of 0.5%, while hedge fund B earns an average rate of return of 3.0% per year with a standard deviation of 2.0\%. Which is more unusual, Hedge fund A earning a 4.0% return or hedge fund B earning a return -1.0% return? Why?^[Hint: Standardize the two hedge funds.]

# 4

A discrete random variable $X$ has the following pdf:

```{r, echo=FALSE, results="asis"}
tribble(
  ~x, ~`p(x)`,
  10, 0.10,
  20, 0.20,
  30, 0.30,
  40, 0.40
  ) %>%
  pandoc.table(justify = "ll")
```

@@

# 5

The random variable $Y$ is normally distributed with a mean of 50 and standard deviation of 12

@@

a. What is the $Z$-score for $Y=74$?
b. In your own words, what does this $Z$-score mean?
c. What is the probability that $Y$ takes on a value *greater* than 74?

# 6

On a scale of 1 (least) to 10 (most), how anxious are you about this class? Feel free to share any specific anxieties (they have a better chance to be specifically addressed if you do!).

# 7

On a scale of 1 (least) to 10 (most), how familiar would you say you are with computer programming and/or statistical software?

# 8

List any statistical software packages (e.g. R, Microsoft Excel, Stata, SAS, SPSS, Minitab, etc.) and any programming languages (e.g. html, php, C/++, Python, LaTeX, etc.) you have had any experience with, and rate your proficiency between 1 (least) and 5 (most), if applicable.

>>>>

---
title: "Preliminary Survey on Statistics and Software"
author: "Ryan Safner"
date: "ECON 480 Fall 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
library("tidyverse")
```

@@

@@

### 1. Using the following sample data:

@@

### a. Find the median. 
### b. Calculate the sample mean, $\bar{x}$
### c. Calculate the sample standard deviation, $s$

\clearpage

### 2. For a fair, six-sided die:

### a. What is the probability of rolling a 5?
### b. What is the probability of rolling an even number?
### c. What is the probability of rolling an even number or a 3?
### d. If you have two fair dice, what is the probability of rolling a 6 on both dice?

\clearpage

### 3. Hedge fund A earns an average rate of return of 2.5% per year with a standard deviation of 0.5%, while hedge fund B earns an average rate of return of 3.0% per year with a standard deviation of 2.0\%. Which is more unusual, Hedge fund A earning a 4.0% return or hedge fund B earning a return -1.0% return? Why?^[Hint: Standardize the two hedge funds.]

\clearpage

### 4. A discrete random variable $X$ has the following pdf:

```{r, echo=FALSE, results="asis"}
tribble(
  ~x, ~`p(x)`,
  10, 0.10,
  20, 0.20,
  30, 0.30,
  40, 0.40
  ) %>%
  knitr::kable(., "latex")
```

@@

\clearpage

### 5. The random variable $Y$ is normally distributed with a mean of 50 and standard deviation of 12

@@

### a. What is the $Z$-score for $Y=74$?
### b. In your own words, what does this $Z$-score mean?
### c. What is the probability that $Y$ takes on a value *greater* than 74?

\clearpage

### 6 On a scale of 1 (least) to 10 (most), how anxious are you about this class? Feel free to share any specific anxieties (they have a better chance to be specifically addressed if you do!).

\vspace{2in}

### 7. On a scale of 1 (least) to 10 (most), how familiar would you say you are with computer programming and/or statistical software?

\vspace{2in}

### 8. List any statistical software packages (e.g. R, Microsoft Excel, Stata, SAS, SPSS, Minitab, etc.) and any programming languages (e.g. html, php, C/++, Python, LaTeX, etc.) you have had any experience with, and rate your proficiency between 1 (least) and 5 (most), if applicable.
